---
title: "Simple document"
output: html_document
---

```{r, message = FALSE}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is going to be a plot! Frist I generate a dataframe, then use ggplot to make a scatterplot.

```{r, echo = FALSE}
plot_df =
  tibble(
    x = rnorm(n=1000),
    y = 1+2*x+rnorm(n=1000)
  )
ggplot(plot_df, aes(x=x, y=y)) +geom_point()
```

## Plot for learning assessment

```{r test_code_chunk}
library(tidyverse)
plot_df =
  tibble(
    x = rnorm(n=500, mean=1),
    logVar = x > 0,
    abs_normal = abs(x)
  )
ggplot(plot_df, aes(x=abs_normal)) + geom_histogram()

median_samp = median(pull(plot_df, x))
```

# Section 4 

Cheat Sheet for Text Formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell








